### 2020-12-31 ch/2-related-work.tex
Continue literature review

\citet{kim2019learning} also consider the problem of learning from biased data (and evaluating on unbiased data).
While they do not formulate the problem as a fairness problem,
it is equivalent to enforcing fairness in the presence of severe sampling bias.
Their main motivating example is the Colored MNIST dataset:
in this dataset, digits are randomly colored in the test set,
but in the training set there is a one-to-one correspondence between digit class and color.
A na\"ive classifier will learn to predict color instead of digit class.

>>>>

\citet{kim2019learning} also consider the problem of learning from biased data (and evaluating on unbiased data).
While they do not formulate the problem as a fairness problem,
it is equivalent to enforcing fairness in the presence of severe sampling bias.
Their main motivating example is the Colored MNIST dataset:
in this dataset, digits are randomly colored in the test set,
but in the training set there is a one-to-one correspondence between digit class and color.
A na\"ive classifier will learn to predict color instead of digit class.
The proposed method is very similar to \citet{ganin2016domain} and \citet{edwards2016censoring},
if we think of the colors as forming different domains
(\ie, the \emph{red} domain contains all red digits, etc).
The goal is then to learn a domain-independent representation.
The main difference to previous work is an additional entropy loss term in the adversarial loss.

\citet{arjovsky2019invariant} tackle a similar problem, but take a very different approach,
which they term ``Invariant Risk Minimization'', in contrast to the default method Empirical Risk Minimization.
They formalize the problem as one of different environments $e\in E$.

\citet{creager2020environment} compares itself directly to \citet{arjovsky2019invariant}.

--- --- --- --- --- ---
